\plaintitle

### 2017-06-04 papers/IoT2017/intro.tex
no message

Power grids are undergoing major changes due to rapid
acceleration in renewable energy resources, such as wind and solar power \cite{EIA2014, 5430489}. For example, 
$4,143$ megawatts of solar panels were installed in third quarter of 2016 \cite{seia}. This capacity is estimated to grow from 4\% in 2015 to 29\% in 2040 \cite{Randal}. At the same time the battery technology costs per kWh have been dropping significantly \cite{stock2015powerful}, reaching grid parity \cite{bronski2015economics}. This massive integration of renewable energy requires detailed information and visibility into all aspects of this network, making it difficult to manage, especially in the presence of variable distributed energy resources \cite{7452738}. Therefore, a different vision for the future of power-grid operations is emerging: a decentralized system in which local communities are arranged in microgrids \cite{rahimi2012transactive}. In this vision, energy generation, transmission, distribution and even storage (e.g., electric vehicles in a community) can be strategically used to balance load and demand spikes.

Furthering the concept of microgrids, transactive energy models have been proposed to support the next distribution system evolution \cite{kok2016society,cox2013structured,melton2013gridwise}. Transactive Energy is a set of market based constructs for dynamically balancing the demand and supply across the electrical infrastructure \cite{melton2013gridwise}. In this approach, customers on the same feeder (i.e. sharing a power line link) can operate in an open market, trading and exchanging generated energy locally. Distribution System Operators can be the custodian of this market, while still meeting the net demand \cite{7462854}. For example, the Brooklyn Microgrid developed by LO3 Energy is a peer-to-peer energy market for locally generated renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}

@@

% connect this back to the challenges described below
Specifcally,

% This is where the RIAPS and computing services discussion will be included. However, it does not solve the following challenges, which is the focus of this paper.
%

% electric grid is changing: renewables, storage capacity, etc. -> prosumers

In order to take advantage of these capabilities, electric grids need to become more decentralized.
% what are the advantages of decentralization?

% transactive microgrid

% there are pilot studies, however, providing privacy is an open problem

Transactive energy may pose a much greater threat to prosumers' privacy than smart metering.
\begin{itemize}
\item Firstly, since prosumers may purchase energy from each other in a transactive microgrid, transactions may inadvertently reveal the prosumers' detailed energy usage patterns to other prosumers within the microgrid.
Addressing this issue in a decentralized trading platform is quite challenging as it requires hiding the identities of trade partners from each other.
In comparison, secure smart metering reveals the prosumers' energy usage patterns only to the provider. 
\item Secondly, transactions may reveal the future energy usage of a prosumer, which could be used to infer private information.
For example, a smart home may know that its inhabitants will go out in the evening (e.g., by looking at their calendar), and it may trade energy futures accordingly in the morning.
Without adequate privacy measures, these trades may reveal to other prosumers in the microgrid that the inhabitants will not be at home later.
Note that energy futures, whose delivery may happen several hours after when the transaction is made, can play a very important role in predicting and controlling microgrid load.
In comparison, smart metering reveals only current (and past) usage.
\item Thirdly, transactions and energy usage data in a transactive microgrid are much richer source of information than the simple energy usage data collected by smart meters.
More specifically, the information available in a transactive microgrid is a superset of what is available from smart metering, and it may be used to infer personal information, such as risk propensity and financial standing.
\end{itemize}

We propose a solution that enables trading energy futures in a secure and verifiable manner, preserves the prosumers' privacy, enables the DSO to regulate the trading platform and enforce certain safety rules.

>>>>

Power grids are undergoing major changes due to rapid
acceleration in renewable energy resources, such as wind and solar power \cite{EIA2014, 5430489}. For example, 
$4,143$ megawatts of solar panels were installed in third quarter of 2016 \cite{seia}. This capacity is estimated to grow from 4\% in 2015 to 29\% in 2040 \cite{Randal}. At the same time, the battery technology costs per kWh have been dropping significantly \cite{stock2015powerful}, reaching grid parity \cite{bronski2015economics}. This massive integration of renewable energy requires detailed information and visibility into all aspects of this network, making it difficult to manage, especially in the presence of variable distributed energy resources \cite{7452738}. Therefore, a different vision for the future of power-grid operations is emerging: a decentralized system in which local communities are arranged in microgrids \cite{rahimi2012transactive}. In this vision, energy generation, transmission, distribution and even storage (e.g., electric vehicles in a community) can be strategically used to balance load and demand spikes.

Furthering the concept of microgrids, transactive energy models have been proposed to support the next distribution system evolution \cite{kok2016society,cox2013structured,melton2013gridwise}. Transactive energy is a set of market based constructs for dynamically balancing the demand and supply across the electrical infrastructure \cite{melton2013gridwise}. In this approach, customers on the same feeder (i.e. sharing a power line link) can operate in an open market, trading and exchanging generated energy locally. Distribution System Operators (DSO) can be the custodian of this market, while still meeting the net demand \cite{7462854}. For example, the Brooklyn Microgrid, which was developed by LO3 Energy as a pilot project, is a peer-to-peer energy market for locally generated renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}

@@

% This is where the RIAPS and computing services discussion will be included. However, it does not solve the following challenges, which is the focus of this paper.

% connect this back to the challenges described below
Specifically, 
in order to take advantage of local energy production and storage capabilities, 
%in order to take advantage of these capabilities, 
electric grids need to become more decentralized.
However, a decentralized transactive energy system may pose a much greater threat to prosumers' privacy than existing smart metering systems.
\begin{itemize}
\item Firstly, since prosumers\footnote{We refer to customers as \emph{prosumers} to emphasize that they can not only consume energy, but may also produce it.}  may purchase energy from each other in a transactive microgrid, transactions may inadvertently reveal the prosumers' detailed energy usage patterns to other prosumers within the microgrid.
Addressing this issue in a decentralized trading system is quite challenging as it requires hiding the identities of trade partners from each other.
In comparison, secure smart metering reveals the prosumers' energy usage patterns only to the provider. 
\item Secondly, transactions may reveal the future energy usage of a prosumer, which could be used to infer private information.
For example, a smart home may know that its inhabitants will go out in the evening (e.g., by looking at their calendar), and it may trade energy futures accordingly in the morning.
Without adequate privacy measures, these trades may reveal to other prosumers in the microgrid that the inhabitants will not be at home later.
Note that energy futures, whose delivery may happen several hours after when the transaction is made, can play a very important role in predicting and controlling microgrid load.
In comparison, smart metering reveals only current (and past) usage.
\item Thirdly, transactions and energy usage data in a transactive microgrid are much richer source of information than the simple energy usage data collected by smart meters.
More specifically, the information available in a transactive microgrid is a superset of what is available from smart metering, and it may be used to infer personal information, such as risk propensity and financial standing.
\end{itemize}

Before transactive energy system can be deployed in practice, we must address these privacy issues.
However, this is a challenging task, as the system also has to satisfy security and safety requirements, which often conflict with privacy goals.
For example, to prevent a prosumer from destabilizing the grid through careless of malicious energy trading, the system must check all of the prosumers' transactions.
In a decentralized system, this requires disseminating information, which could be used to infer the prosumer's future energy consumption.

In this paper, we propose a system that enables trading energy futures in a secure and verifiable manner, preserves the prosumers' privacy, and enables the DSO to regulate the trading platform and enforce certain safety rules.
\todo{Since SIGCHI does not have section numbers, this paragraph, which describes the organization of the paper, is not very clear.}
First, we describe the basic elements of a transactive microgrid, and we formulate security, safety, and privacy requirements. 
Then, we introduce a decentralized system for transactive microgrids based on distributed ledgers, and describe in detail the transactions and services that are used to implement this system.
Next, we discuss how the system satisfies the security, safety, and privacy requirements.
Finally, we give a brief overview of related work and offer concluding remarks.

### 2017-06-04 papers/IoT2017/prelim.tex
no message

Here, we describe a basic system model for a transactive microgrid based on a distributed ledger, such as a blockchain.
% - smart meters
% - distributed ledger, such as blockchain

\subsubsection{Distributed Ledger}
The distributed ledger stores transactions that specify energy trades, change regulatory policies for the microgrid, etc.
Since the ledger is maintained by multiple ledger nodes, a key implementation requirement is reaching consensus on which transactions are valid and stored in the ledger.
This consensus must be reached quickly, reliably, and securely even in the presence of erroneous or even malicious ledger nodes.
We treat the consensus algorithm as a pluggable module, which can be based on blockchains with proof-of-stake consensus or Practical Byzantine Fault Tolerance algorithm~\cite{castro1999practical}.

@@

@@

\subsubsection{Security}
Prosumers (or outside attackers) should not be able to tamper with measured energy production and consumption values, with financial balances, with other prosumers' bids.

\subsubsection{Safety}
A careless or malicious prosumer may destabilize the grid by promising to produce (or consume) a large amount of energy, but failing to deliver.
Trades which are unlikely to be delivered and would result in a gap between actual production and demand should be prevented.

\subsubsection{Privacy} 
Energy trading should not compromise the privacy of prosumers.
More specifically, prosumers' private information, including energy consumption and production values, are available only to the DSO.

>>>>

Here, we describe a basic system model of a transactive microgrid based on a distributed ledger, such as a blockchain.

\subsubsection{Distributed Ledger}
% - energy trades must be stored on a ledger (to prevent malleability)
% - distributed ledger for reliability
The distributed ledger stores transactions that specify energy trades, change regulatory policies for the microgrid, etc.
Since the ledger is maintained by multiple ledger nodes, a key implementation requirement is reaching consensus on which transactions are valid and stored in the ledger.
This consensus must be reached quickly, reliably, and securely even in the presence of erroneous or even malicious ledger nodes.
% actually, we simply don't care about the consensus mechanism in this paper
We treat the consensus algorithm as a pluggable module, which can be based on blockchains with proof-of-stake consensus or Practical Byzantine Fault Tolerance algorithm~\cite{castro1999practical}.

@@

\subsubsection{Smart Meters}
\TODO{measures energy production / consumption}
\TODO{may record energy production / consumption on the ledger or directly report it to the DSO}

@@

\subsubsection{Security}
Prosumers (or outside attackers) should not be able to tamper with measured energy production and consumption values, with financial balances, with other prosumers' bids.
\TODO{ensure correct billing (i.e., prosumer cannot tamper with energy production / consumption or financial balances of any prosumer)}
\TODO{ensure that prosumers cannot back out of trades unilaterally, or tamper with other prosumers trading or bids}
\TODO{ensure that prosumers cannot change policies that are to be set by the DSO for the microgird}
\TODO{impact of node compromise is limited, and can be mitigated (i.e., offending node may be removed)}

\subsubsection{Safety}
A careless or malicious prosumer may destabilize the grid by promising to produce (or consume) a large amount of energy, but failing to deliver.
\TODO{this could destabilize the microgrid, or even the main grid}
Trades which are unlikely to be delivered and would result in a gap between actual production and demand should be prevented.
\TODO{net amount of energy sold (or bought) by a prosumer is limited (by a constant set by the DSO), where net amount of energy sold is the difference between the amount of energy sold and bought (net amount of energy bought is defined analogously)}
\TODO{energy bids posted by the prosumer are limited in the same way}

\subsubsection{Privacy} 
Energy trading should not compromise the privacy of prosumers.
More specifically, prosumers' private information, including energy consumption and production values, are available only to the DSO.
\TODO{other prosumers should not be able to tell how much energy was consumed / produced by a prosumer, or what bids the prosumer has posted (or with whom the prosumer traded}
